On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-08-30 Manuscript/manuscript.tex

@@

An additional simulation study in which block bootstrap is used to estimate 
parameters of an AR(1) process with an underlying exponential marginal 
distribution is discussed in the Appendix. Overall, the results with an 
underlying marginal exponential distribution are very similar to the results 
with an underlying normal distribution discussed above.

>>>>

\jy{What was $B$?}

@@

An additional simulation study in which block bootstrap is used to estimate
\jy{not an AR(1) process...}
parameters of an AR(1) process with an underlying exponential marginal 
distribution is discussed in the Appendix. Overall, the results with an 
underlying marginal exponential distribution are very similar to the results 
with an underlying normal distribution discussed above.
